Language-Based Security for Low-Level MPC

### 2024-05-22 ppdp24/example-bdoz.tex
checkpoint

We can capture both the preliminary distribution of Beaver triples and BDOZ shares
as a pre-processing predicate that establishes conditions for initial
memories (see Definition \ref{def-progtt}).  Here we assume two input
secrets $\elab{\secret{x}}{1}$ and $\elab{\secret{y}}{2}$ and a single
Beaver Triple to compute $\elab{\secret{x}}{1} \ftimes
\elab{\secret{y}}{2}$, but we can extend this for additional gates.
As for GMW, we use $\macgv{\mesg{w}}$ to refer to secret-shared values
reconstructed with addition, where by convention shares are message
values $\elab{\mesg{w}}{\cid}$ for all $\cid$.
\begin{definition}[BDOZ preprocessing]
  Define:
  \begin{mathpar}
    \mathit{shares} \defeq
    \{ \elab{\mesg{w}}{\cid}\ |\ \cid \in \{ 1, 2 \} \wedge w \in \{ a,b,c,x,y \}  \}

>>>>

We can capture both the preliminary distribution of Beaver triples and BDOZ shares
as a pre-processing predicate that establishes conditions for initial
memories (see Definition \ref{def-aprogtt}).  Here we assume two input
secrets $\elab{\secret{x}}{1}$ and $\elab{\secret{y}}{2}$ and a single
Beaver Triple to compute $\elab{\secret{x}}{1} \ftimes
\elab{\secret{y}}{2}$, but we can extend this for additional gates.
As for GMW, we use $\macgv{\mesg{w}}$ to refer to secret-shared values
reconstructed with addition, where by convention shares are message
values $\elab{\mesg{w}}{\cid}$ for all $\cid$.
\begin{definition}[BDOZ preprocessing]
  Define:
  \begin{mathpar}
    \mathit{shares} \defeq
    \{ \elab{\mesg{w}}{\cid}\ |\ \cid \in \{ 1, 2 \} \wedge w \in \{ a,b,c,x,y \}  \}

### 2024-05-22 ppdp24/model.tex
checkpoint

It is necessary to add $\bot$ to the range of memories since
the possibility of abort needs to be reflected in adversrarial
runs of a protocol. We can define $\aruns(\prog,\adversary)$
as the ``prefix'' memories that result from possibly-aborting
protocols, but we also need to ``pad out'' the memories
of partial runs with $\bot$, as we defin in $\botruns(\prog,\adversary)$,
to properly reflect the contents of views and outputs even in case of abort. 
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given program $\prog$ with $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$, and
  any assumed pre-processing predicate $\preproc$ on memories, define:
  $$
  \begin{array}{c}
    \aruns(\prog) \defeq \\
    \{ \store \mid \exists \store_1 \in \mems(R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \cap \store_2,\prog) \aredxs (\store,\varnothing) \}
  \end{array}
  $$
  where by default, $\preproc(\store) \iff \dom(\store) = S$, and also define the following
  which pads out undefined views and outputs with $\bot$:
  $$
  \begin{array}{l}
    \botruns(\prog) \defeq \\
    \qquad \{ \store\{ x_1 \mapsto \bot, \ldots, x_n \mapsto \bot \} \mid \\
    \qquad \phantom{\{} \store \in \aruns(\prog) \wedge \{ x_1,\ldots,x_n\} = (V \cup O) - \dom(\store) \}
  \end{array}
  $$
  Then the \emph{$\adversary$ distribution of $\prog$}, written $\progtt(\prog,\adversary)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\prog,\adversary) =  1 / |\botruns(\prog)| \ \text{if}\ \store \in \botruns(\prog), \text{otherwise}\ 0
  $$
\end{definition}

>>>>

It is necessary to add $\bot$ to the range of memories since
the possibility of abort needs to be reflected in adversrarial
runs of a protocol. We can define $\aruns(\prog,\adversary)$
as the ``prefix'' memories that result from possibly-aborting
protocols, but we also need to ``pad out'' the memories
of partial runs with $\bot$, as we defin in $\botruns(\prog,\adversary)$,
to properly reflect the contents of views and outputs even in case of abort. 
\begin{definition}
  \label{def-aprogd}
  \label{def-aprogtt}
  \label{definition-aprogd}
  Given program $\prog$ with $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$, and
  any assumed pre-processing predicate $\preproc$ on memories, define:
  $$
  \begin{array}{c}
    \aruns(\prog) \defeq \\
    \{ \store \mid \exists \store_1 \in \mems(R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \cap \store_2,\prog) \aredxs (\store,\varnothing) \}
  \end{array}
  $$
  where by default, $\preproc(\store) \iff \dom(\store) = S$, and also define the following
  which pads out undefined views and outputs with $\bot$:
  $$
  \begin{array}{l}
    \botruns(\prog) \defeq \\
    \qquad \{ \store\{ x_1 \mapsto \bot, \ldots, x_n \mapsto \bot \} \mid \\
    \qquad \phantom{\{} \store \in \aruns(\prog) \wedge \{ x_1,\ldots,x_n\} = (V \cup O) - \dom(\store) \}
  \end{array}
  $$
  Then the \emph{$\adversary$ distribution of $\prog$}, written $\progtt(\prog,\adversary)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\prog,\adversary) =  1 / |\botruns(\prog)| \ \text{if}\ \store \in \botruns(\prog), \text{otherwise}\ 0
  $$
\end{definition}
